Bayes Exploration with Brms

### 2023-08-12 Analysis/e1_brms_test.qmd
google sync, new posterior function

@@

>>>>

testExtrap <- e1 |> filter(expMode=="test-Nf")

@@

dist_gauss_trunc0 <- brm(dist|trunc(lb=0) ~ 1+vb*condit + (0+vb|id),data=testExtrap,family=gaussian(), iter=2000, control=list(adapt_delta=0.92, max_treedepth=13), chains=3, file=paste0(here::here("data/model_cache","gauss_t_vbCondit_dist_extrap_ml6")), silent=0);

gauss_trunc0 <- brm(vx|trunc(lb=0) ~ 1+vb*condit + (0+vb|id),data=testExtrap,family=gaussian(), iter=2000, control=list(adapt_delta=0.92, max_treedepth=13), chains=3, file=paste0(here::here("data/model_cache","gauss_t_vbCondit_vx_extrap_ml6")), silent=0);

### 2023-08-12 Analysis/e1_discrim.qmd
google sync, new posterior function

```{r setup}
pacman::p_load(tidyverse,tidybayes,brms,broom,broom.mixed,lme4,emmeans,here,knitr,kableExtra,gt,gghalves,patchwork,ggforce,ggdist)
e1 <- readRDS(here("data/e1_08-04-23.rds"))
source(here("Functions/Display_Functions.R"))

@@

options(mc.cores = 4, brms.backend = "cmdstanr")
m1_bayes <- brm(vx ~ 1 + bandInt + condit + (1 + bandInt | id), data = test, family = gaussian())
summary(m1_bayes)

>>>>

```{r setup}
pacman::p_load(tidyverse,tidybayes,brms,broom,broom.mixed,lme4,emmeans,here,knitr,kableExtra,gt,gghalves,patchwork,ggforce,ggdist,equatiomatic)
e1 <- readRDS(here("data/e1_08-04-23.rds"))
source(here("Functions/Display_Functions.R"))

@@

options(mc.cores = 4, brms.backend = "cmdstanr")

m1_bayes <- brm(vx ~ 1 + bandInt + condit + (1 + bandInt | id), data = test, family = gaussian())
summary(m1_bayes)

### 2023-08-12 Misc/Visuals_Interactives/ALM_Shiny.qmd
google sync, new posterior function

---
title: Shiny App
# format: 
#   html:
#     page-layout: custom
code-fold: true
code-tools: true
toc: true
execute: 
  warning: false
---

>>>>

---
title: ALM Shiny App Code
date: last-modified
categories: [Simulation,ALM,EXAM,Shiny,Interactive,R]
# format: 
#   html:
#     page-layout: custom
code-fold: true
code-tools: true
toc: true
execute: 
  warning: false
---

### 2023-08-12 Misc/scratch/.ipynb_checkpoints/bayes_explore-checkpoint.qmd
google sync, new posterior function

```{r setup}
pacman::p_load(tidyverse,tidybayes,brms,broom,broom.mixed,lme4,emmeans,here,knitr,kableExtra,gt,gghalves,patchwork,ggforce,ggdist)
e1 <- readRDS(here("data/e1_08-04-23.rds"))
source(here("Functions/Display_Functions.R"))
source(here("Functions/org_functions.R"))

test <- e1 |> filter(expMode2 == "Test")

 test <- test |> mutate(id=factor(id,levels=unique(id)),
         vxbn=vxb/max(test$vxb),vxn=vx/max(test$vx),bandIntn=bandInt/max(test$vx),bandIntnb=bandInt/max(test$vxb),svx=scale(vx, scale = TRUE),
         vxC=ifelse(vx>2000,2000,vx))

@@

fit_int_norm <- brm(vx ~ 1+bandInt+(1|id), # 2.1 sec execution time with 4 cores
  data = test,
  family = gaussian(),
  prior = c(
    prior(normal(800, 10), class = Intercept),
    prior(normal(400, 10), class = sigma)
  )
)
bayesplot::ppc_dens_overlay_grouped(test$vx,
  yrep = posterior_predict(fit_int_norm, ndraws = 100),
  group = test$bandInt
)

bandId_norm_vxC <- brm(vxC ~ 1+bandInt+(1|id), # 2.1 sec execution time with 4 cores
  data = test,
  family = gaussian(),
  prior = c(
    prior(normal(800, 10), class = Intercept),
    prior(normal(400, 10), class = sigma)
  )
)

bayesplot::ppc_dens_overlay_grouped(test$vx,
  yrep = posterior_predict(bandId_norm_vxC, ndraws = 100),
  group = test$bandInt
)
```

loo_fit<- loo(fit_int_norm,bandId_norm_vxC)
loo_fit$diffs %>% as.data.frame() %>% round(1)

loo_R2(fit_int_norm)
loo_R2(bandId_norm_vxC)

loo_comp <- loo_compare(list(vx = loo(fit_int_norm), 
                             vxC = loo(bandId_norm_vxC)))
loo_comp
1 - pnorm(-loo_comp[2,1], loo_comp[2,2])

@@

test_int_vx <- run_model(brm(vx~1,data=test),modelName = "test_int_vx")
test_int_vx3 <- brm(vx~1,data=test,file=paste0(here::here("data/model_cache"),"/test_int_vx"))

@@

IRT style
```{r}

fit_b_irt <- brm(vxC ~ 1+(1|bandInt)+ (1 | id), 
  data = test,
  family = gaussian(),
  prior = c(
    prior(normal(600, 200), class = Intercept),
    prior(normal(300, 10), class = sigma)
)
)
fit_b_irt

coef(fit_b_irt)$id %>% as_tibble(rownames="id") %>% select(id, starts_with("Est")) |> print(n=15)
coef(fit_b_irt)$bandInt %>% as_tibble(rownames="bandInt")

fit_dist_irt <- brm(dist ~ 1+(1|bandInt)+ (1 | id), 
  data = test,
  family = gaussian(),
  prior = c(
    prior(normal(600, 200), class = Intercept),
    prior(normal(300, 10), class = sigma)
)
)
fit_dist_irt
coef(fit_dist_irt)$id %>% as_tibble(rownames="id") %>% select(id, starts_with("Est")) |> print(n=15)
coef(fit_dist_irt)$bandInt %>% as_tibble(rownames="bandInt")

fit_distCondit_irt <- brm(dist ~ 1+condit+(1|bandInt)+ (1 | id), 
  data = test,
  family = gaussian(),
  prior = c(
    prior(normal(600, 200), class = Intercept),
    prior(normal(300, 10), class = sigma)
)
)
coef(fit_distCondit_irt)$bandInt %>% as_tibble(rownames="bandInt") 
coef(fit_distCondit_irt)$id %>% as_tibble(rownames="id") %>% select(id, starts_with("Est")) |> print(n=15)

```
coef(fit_b_irt)$bandInt %>% as_tibble(rownames="bandInt")

bandInt Estimate.Intercept Est.Error.Intercept Q2.5.Intercept Q97.5.Intercept
  <chr>                <dbl>               <dbl>          <dbl>           <dbl>
1 100                   595.                18.7           560.            633.
2 350                   716.                18.8           680.            754.
3 600                   826.                18.7           789.            863.
4 800                  1023.                20.1           984.           1064.
5 1000                 1167.                20.2          1128.           1207.
6 1200                 1260.                20.5          1220.           1299.

coef(fit_dist_irt)$bandInt %>% as_tibble(rownames="bandInt") 
# A tibble: 6 × 5
  bandInt Estimate.Intercept Est.Error.Intercept Q2.5.Intercept Q97.5.Intercept
  <chr>                <dbl>               <dbl>          <dbl>           <dbl>
1 100                   326.                13.7           300.            354.
2 350                   243.                13.7           217.            271.
3 600                   195.                13.7           169.            222.
4 800                   207.                15.0           178.            237.
5 1000                  227.                15.2           197.            256.
6 1200                  269.                15.3           240.            300.

>>>>

```{r setup}
pacman::p_load(tidyverse,tidybayes,brms,broom,broom.mixed,lme4,emmeans,here,knitr,kableExtra,gt,gghalves,patchwork,ggforce,ggdist)
e1 <- readRDS(here("data/e1_07-27-23.rds"))
source(here("Functions/Display_Functions.R"))
source(here("Functions/org_functions.R"))

test <- e1 |> 
  filter(expMode2 == "Test") |> 
  mutate(id=factor(id,levels=unique(id)),
         vxbn=vxb/max(test$vxb),vxn=vx/max(test$vx),bandIntn=bandInt/max(test$vx),bandIntnb=bandInt/max(test$vxb),svx=scale(vx, scale = TRUE),
         vxC=ifelse(vx>2000,2000,vx))

@@

Unrealistic priors
```{r}
#| eval: false

fit_int_unif <- brm(vx ~ 1, # 170.4 sec execution time with 8 cores
  data = test,
  family = gaussian(),
  prior = c(
    prior(uniform(-10^6, 10^6),
          class = Intercept,
          lb = -10^6,
          ub = 10^6),
    prior(uniform(0, 10^6),
          class = sigma,
          lb = 0,
          ub = 10^6)
  ),
  iter = 3000,
  control = list(adapt_delta = .99,
                 max_treedepth = 15),
  file="cache/fit_int_unif"
)

fit_int_unif

```
 Family: gaussian 
  Links: mu = identity; sigma = identity 
Formula: vx ~ 1 
   Data: test (Number of observations: 10109) 
  Draws: 4 chains, each with iter = 3000; warmup = 1500; thin = 1;
         total post-warmup draws = 6000

Population-Level Effects: 
          Estimate Est.Error l-95% CI u-95% CI Rhat Bulk_ESS Tail_ESS
Intercept   835.95      4.45   827.48   844.81 1.00     3927     2927

Family Specific Parameters: 
      Estimate Est.Error l-95% CI u-95% CI Rhat Bulk_ESS Tail_ESS
sigma   435.94      3.30   429.37   442.35 1.01      487      576

@@

@@
